### 2020-04-08 Proposal/aws_325ghz_proposal.tex

\noindent
\textbf{{\LARGE Arctic Weather Satellite (AWS) channels\\definition: Work plan}}  \vspace{5mm}\\
{\bf Patrick Eriksson}\\
Dept.\ of Space, Earth and Environment\\
Chalmers University of Technology\\
SE-412\,96, Gothenburg, Sweden \vspace{10mm}

>>>>

\noindent
\textbf{{\Large Arctic Weather Satellite (AWS) channels definition:\\Work plan}}  \vspace{5mm}\\
{\bf Patrick Eriksson}\\
Dept.\ of Space, Earth and Environment\\
Chalmers University of Technology\\
SE-412\,96, Gothenburg, Sweden \vspace{10mm}
